Effective collector efficiency of sparse and dense arrays of cylindrical collectors in transitional turbulence

### 2020-07-15 drafts/outline.tex
in prog

\title{Modeling effective collector efficiency of sparse and dense arrays of cylindrical collectors in varying states of flow velocity and turbulence}

@@

\paragraph{Editing notes:}

\textcolor{green!50!red}{Parenthetical insertions in this color are author/editor notes referring to the preceding word or phrase}

\paragraph{Figures:}

I'm aiming for 10-12 figures; 3 methods, 7 results or thereabouts

\begin{itemize}

\item Methods: Direct interception and capture efficiency diagram

\marginpar{Borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}

\begin{figure}[h]
\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
\centering
\caption{Particle capture efficiency diagram}
\end{figure}

\item Methods: Particle size distribution

\item Methods: Flume floorplan

The figure from the grant proposal has a few features different from the experimental setup. TODO: I'm going to look in the flume manual for a blueprint

\end{itemize}

@@

TODO\\
\hfill\break
Example citation \citep{Fauria_2015}.

@@

In this study, we focus on direct interception of suspended particles by submerged vegetation. Direct interception is the adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants). This is just one of many fluid dynamics mechanisms that act on suspended particles. Others include gravitational settling, inertial impaction, and diffusional deposition. Gravitational settling is the process of particles denser than water being drawn towards and coming to rest on the channel bottom. Inertial impaction and diffusional deposition are other means by which suspended particles can adhere to collectors. Inertial impaction occurs when particles possess momentum relative to streamlines, and diffusional deposition arises due to some combination of turbulence and Brownian motion.

In transitionally turbulent flows ($1 < Re_c < 10^3$), which

@@

@@

TODO\\
\hfill\break
The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$. The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$). However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.

>>>>

\title{Effective collector efficiency of sparse and dense arrays of cylindrical collectors in transitional turbulence}

@@

@@

@@

In this study, we focus on direct interception of suspended particles by submerged vegetation. Direct interception is the adhesion of particles traveling along streamlines to the surfaces of collectors (e.g., plants). This is just one of several fluid dynamics mechanisms that act on suspended particles. Others include gravitational settling, inertial impaction, and diffusional deposition. Gravitational settling is the process of particles denser than water being drawn towards and coming to rest on the channel bottom. Inertial impaction and diffusional deposition are other means by which suspended particles can adhere to collectors. Inertial impaction occurs when particles possess momentum relative to streamlines, and diffusional deposition arises due to some combination of turbulence and Brownian motion.

Capture efficiency ($\eta=\frac{b_c}{d_c}$) is defined as the ratio between the upstream width ($b_c$) of the streamlines that encounter a collector and the collector's own diameter ($d_c$), which may be represented by an effective length in the case of non-cylindrical collectors (Figure 1).

\marginpar{Figure borrrowed from Fauria 2015. We should ask her permission before submitting, correct? Also, if we should make our own or swap in a different figure, let me know.}

\begin{figure}[h]
\includegraphics[width=10cm]{fauria particle capture efficiency diagram.jpg}
\centering
\caption{Particle capture efficiency diagram (TODO caption)}
\end{figure}

Particle capture in transitionally turbulent flows ($1<\Rey<1000$), which occur commonly in the environments and on the length scales of aquatic macrovegetation, does not follow the analytical expressions involving Reynolds number, collector diameter, and particle diameter ($d_p$), derived for creeping flow. Hence, empirical estimates must be used. \citet{Palmer_2004} introduced a power law expression for estimating capture efficiency of cylindrical collectors of the form $$\eta=C\Rey_c^{a}R^{b}\,,$$ where $\Rey_c=\frac{ud_c}{\nu}$, $u$ is flow velocity, $\nu$ is kinematic velocity, and $R=\frac{d_c}{d_p}$ is the ratio between collector diameter and particle diameter ($d_p$).

@@

TODO: Flume floorplan figure

@@

TODO\\
\hfill\break
The assumption that probability of retention ($p_r$) is 100\% when stems are coated with grease might be questionable based on our result that biofilm increased $\eta\prime$ in comparison to greased dowels. The only other effect of biofilm that is readily apparent to me is perhaps increasing effective stem diameter ($d_c$). However, with our model for Reynolds number ($\Rey_c \propto d_c$), and both us and \citet{Fauria_2015} finding $\eta\prime \sim -\Rey_c$, increasing stem diameter would be expected to have the opposite effect, unless I'm missing something.
